Influence bias in cultural evolutionary dynamics

### 2023-11-05 ms/ms.tex
update

% Title page
\title{Prestige bias in cultural evolutionary dynamics}
% Authors
\renewcommand\Affilfont{\small}

@@

\begin{abstract}
{If the traits of more successful individuals are more likely to be adopted, the resulting cultural transmission is described as being success-biased. Prestige may be used as a proxy for success.}
Here, we model prestige bias as a combination of indirect success bias and influence bias, the latter meaning that the choice of a role-model depends on the number of individuals that have already copied  that role-model.
{The} effect of prestige on cultural evolutionary dynamics {is analyzed} using mathematical analysis and stochastic simulations.
{Analytic} approximations to the stochastic role-model choice process {facilitate the} mathematical analysis and reduce the computational complexity of simulations. {Approximations are given}  to the fixation probability and the fixation time of an invading cultural trait in different environments. 
We show that indirect success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.	
Influence bias{, which may be strong in communities where social media are prevalent,}  also accelerates the evolutionary dynamics, as can be expected in a rich-{get}-richer process.
\end{abstract}

@@

%\paragraph{Cultural transmission.}
%In cultural transmission, individuals transmit cultural traits (i.e., behaviors, beliefs, norms) to one another, typically by learning and demonstrating \citep{transmissionVectorsBook}.
%Examples for cultural traits in humans are norms, preferences, tools, ideas, and language, potentially transmitted verbally and/or by observations \citep{transmissionVectors}. 
%Although cultural transmission is common in humans, it is also observed in other animals, e.g. chimpanzees \citep{chimpsPrestige, chimpsCopy}, dolphins and whales \citep{dolphins_whales}, elephants \citep{elepahntsRepo}, and even flies \citep{fliesPaper} and fish \citep{Truskanov2020}.

@@

To distinguish this form of indirect bias from other definitions of prestige, we call it \emph{influence bias}.
This is an important distinction, as influence is a context-dependent bias, rather than a content-{dependent} bias: it does not depend on the phenotype itself but rather on the number of copiers that have already copied each role-model, which may be easier and more accurate to estimate than success. 
Influence bias is also frequency independent (see \Cref{cor:GBD} below), and thus it differs from conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.

@@

In the following, we develop a stochastic model of cultural transmission with prestige bias that combines both cross-domain indirect success bias and influence bias.
We develop analytic approximations for this model and analyze its dynamics. We also find approximations for the probability and time to fixation of a `successful' phenotype (i.e., that is {subject to} success bias). Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and influence bias play the role of natural selection and genetic drift, respectively.

@@

\paragraph{Influence bias.}
Here we introduce a new element to the model by assuming that in each generation, copiers choose their role-models one by one.
We formulate this assumption in the following.
{Denote by} $K_{i,j}$  the number of copiers that {choose} role-model $j$ after copier $i$ chose a role-model. Thus, $i$ out of $N$ copiers {had} already {chosen} a role-model, $\sum_{j=1}^N{K_{i,j}} = i$, and there are $N-i$ copiers that have yet to choose a role-model.
The stochastic process of role-model choice, 
\begin{equation} \label{eq:process}
\big\{\vec{K}_i = (K_{i,1}, \ldots, K_{i,N}) \big\}_{i=1}^N \;,
\end{equation}
is described by the recurrence equation
\begin{equation} \label{eq:recurrence}
K_{i,j} = K_{i-1,j} + S_{i,j}, \quad i,j=1,2,\ldots,N \;,
\end{equation}
where $S_{i,j}=1$ if the $i$-th copier chose role-model~$j$ and 0 otherwise, and the initial state is $K_{0,j}=0$.

Following \cref{eq:ourF}, the probability that the $i$-th copier chose role-model $j$ is given by the prestige of role-model $j$ in the eyes of copier $i$,
\begin{equation}\label{eq:recPrestige}
Pr(S_{i,j}=1 \mid S_{1,j},S_{2,j},...,S_{i-1,j}) = G_{i,j} \;.
\end{equation}
The prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by success--the estimated biased trait value $\beta(A_{i,j})$--and influence--the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} with
\begin{equation}\label{eq:prestige}
G_{i,j} = \frac{\alpha_{ij} \cdot \beta(A_{i,j}) + (1-\alpha_{ij}) \cdot K_{i-1,j}}{W_i} \;,
\end{equation}
where $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.

Here, the bias weight $\alpha_{i,j}$ determines the relative weighting of success and influence bias. It is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of direct success vs. influence in the role-model's overall prestige in the eyes of the copier.
Different individuals may evaluate the importance of success and influence differently. Additionally, we assume each role-model displays its influence and success individually. For example, individuals with more followers but lacking skill may emphasize the number of their followers rather than their skill.
Finally, the trait of role-model $j$ estimated by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeTrait}.

@@

(i) the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers, that is,
$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$); and
(ii) the expected number of copiers of each role-model equals its relative biased trait value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated trait value.

@@

From \Cref{cor:GBD} we see that if there is no success bias, meaning $Q_j(1,1)=q$ for $j$ in $1,...,N$, then the expected number of copiers will be Binomial distributed. This proves that influence bias is not frequency dependent.

@@

Frigyik et al.~\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws  (the population size, $N$, in our model) approaches infinity, based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
We therefore have an approximation for the relative prestige each role-model has when evaluated by copiers. Thus, choosing the role-models for all copiers is equivalent to drawing from a {multinomial} distribution where the parameters are the modified weights from a Dirichlet distribution and we have the following corollary.
\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Fixation probability and time}
After finding that the DM distribution is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
We focus on the fixation probability and conditional fixation time (conditioned on the population reaching fixation) of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and influence on prestige bias, given by \cref{eq:prestige}.
For simplicity, we use the dichotomous model, and we do not include role-model estimation error in this analysis, i.e $e_i=0$ for every copier $i$.
As shown above, transmission in our model is approximately DM distributed (\Cref{cor:dirichlet} and \cref{eq:copier_choose}).

@@

The approximation follows the trend of the simulation results for all $\alpha$ values.
{On} increasing the success coefficient {$\alpha$} to more than 0.15, the simulation results were located above the changing environment approximation, and below the constant environment approximation. We believe the reason is the structure of the cycle.
Our proof and approximation in the changing environment are for a large {number} of cycles, and when the success coefficient {$\alpha$} is too high, there might be very few cycles. Either the ideal trait is copied by enough copiers so that the influence is sufficient to negate the success bias when the cycle changes (and the trait favored by the bias becomes the disfavored), or the opposite happens, and the ideal trait {goes} extinct before there {are} enough copiers that copied it.
We then tried to change the ratio between the number of cycles where $\hat{A}$ is favored and disfavored. We showed that the approximation fits well regardless of the ratio, but when the ratio of favored generations to disfavored ones is very high, it is very similar to a constant environment model.

@@

We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal success-bias weight, $\alpha^*$, which minimizes the expected squared error between the chosen trait value and the optimal trait value $\hat{A}$,
\begin{equation}\label{eq:optimal_alpha}
\alpha^* = \emph{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l} (\hat{A}-A_j)^2 \;,
\end{equation}
where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose role-model~$j$.
% TODO statement about fitness

@@

\begin{figure}[h]
    \includegraphics[width=\linewidth]{choose_bias.pdf}
  \caption{
  \textbf{Advantage of an optimal success-bias weight.}
  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process (within a single generation), demonstrating that influence becomes more favored by copiers as more copiers have made their choice.
However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error doesn't decrease, regardless of $\alpha$ or $\eta$.
The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the optimal $\alpha$ model.
Here, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), plots are average of $300$ simulations.}	
  \label{fig:influence_advantage}
\end{figure}

@@

We developed a cultural-evolution model with prestige bias that includes both indirect success and influence biases, where the latter is a bias towards role-models with many copiers.
We model these biases using a stochastic role-model choice process: each copier, in {turn}, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).

@@

%\paragraph{Empirical evidence of prestige bias}
Chudek et al.~\citep{prestige_cultural_learning} report the first direct tests in children that suggest the existence of prestige bias, defined as the tendency to learn from individuals to whom others have preferentially attended, learned, or deferred.
Their definition of prestige is similar to our influence bias. They showed that the odds of 3-4 years-old children learning from an adult role-model to whom bystanders had previously preferentially attended for 10 seconds were more than twice those of learning from a role model whom bystanders ignored.
They also note that prestige effects are domain sensitive: they found that prestigious role-models were attended more when demonstrating artifact use, whereas role-models presenting food preferences had less attendants, suggesting that the domain itself (artifact use vs. food preference) can affect the attendance, and hence the prestige of the role-model.
This led to the suggestion that when the trait is costly to learn individually, prestige will have a stronger bias \citep{prestige_cultural_learning}.
It would be interesting to include costs in our model to try and observe these effects and dynamics in a large population.

@@

%\paragraph{Further work.}
One path forward is an analysis of the dynamics of the adaptive success-bias weight model, in which every copier chooses its $\alpha$. It would be interesting to see the if the mean estimation error and the adaptive weight, $\alpha^*$, {converge} to specific values, and how they are affected by the model parameters.
It may also be possible to relax the assumptions required for our approximations, such as homogeneous estimation error and success-bias weight.
Lastly, it would be interesting to analyze the continuous model and determine how much it differs from the dichotomous model.

@@

@@

\begin{proof}
The initial prestige of role-model $j$ based on \cref{eq:prestige} is
\begin{equation}\label{eq:initial_prob}
G_{1,j} = \frac{\alpha_j\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N} \alpha_m\cdot\beta(A_m+e)} \;.
\end{equation}
The denominator of \cref{eq:initial_prob} can also be formulated as:
\begin{equation}\label{eq:denominator}
 \sum\limits_{m=1}^{N}\alpha_m\beta(A_m+e) = N \cdot \overline{\alpha \cdot \beta(A+e)} \;,
\end{equation}
where $\overline{\alpha\beta(A+e)}$ is the mean value of $\alpha_m\cdot\beta(A_m+e)$.
Using \cref{eq:denominator} and \textbf{Corollary 1} we get,
\begin{equation}
\E[K_{N,j}] = \alpha_j \cdot \beta(A_j+e) \bigg/ \overline{\alpha \cdot \beta(A+e)} \;,
\end{equation}
\end{proof}

>>>>

% Title page
\title{Influence bias in cultural evolutionary dynamics}
% Authors
\renewcommand\Affilfont{\small}

@@

\begin{abstract}
{If the traits of more successful individuals are more likely to be adopted, the resulting cultural transmission is described as being success-biased. Prestige may be used as a proxy for success.}
Here, we model influence bias as a combination of indirect success bias and prestige bias, the latter meaning that the choice of a role-model depends on the number of individuals that have already copied  that role-model.
{The} effect of prestige on cultural evolutionary dynamics {is analyzed} using mathematical analysis and stochastic simulations.
{Analytic} approximations to the stochastic role-model choice process {facilitate the} mathematical analysis and reduce the computational complexity of simulations. {Approximations are given}  to the fixation probability and the fixation time of an invading cultural trait in different environments. 
We show that indirect success bias effectively plays the role of natural selection, whereas prestige bias effectively plays the role of genetic drift.	
Influence bias{, which may be strong in communities where social media are prevalent,}  also accelerates the evolutionary dynamics, as can be expected in a rich-{get}-richer process.
\end{abstract}

@@

@@

{Jimenez \& Mesoudi} (2019) \citep{prestigeSocialLearn} suggest that cultural evolution theory is a major factor in human ecological success. They mention that a way to acquire adaptive social information is by preferentially copying competent individuals within a valuable domain, and they call it success bias as we do in this paper. They also mention that competence within a domain is often difficult or impossible to directly asses, therefore people tend to use indirect cues of success, as suggested by {Henrich and Gil-White}.

In our paper, we examine the effect of both success and prestige biases, and their relationship in contribution to the cultural evolution of populations. We call the joint contribution of both biases \emph{Influence bias}.
This is an important distinction, as prestige is a context-dependent bias, rather than a content-{dependent} bias: it does not depend on the phenotype itself but rather on the number of copiers that have already copied each role-model, which may be easier and more accurate to estimate than success. 
Prestige bias is also frequency independent (see \Cref{cor:GBD} below), and thus it differs from conformity, which depend on the frequency of a trait in the population or in a sample of role-models, rather than the social dynamics of copying.

@@

In the following, we develop a stochastic model of cultural transmission with influence bias that combines both cross-domain indirect success bias and prestige bias.
We develop analytic approximations for this model and analyze its dynamics. We also find approximations for the probability and time to fixation of a `successful' phenotype (i.e., that is {subject to} success bias). Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and influence bias play the role of natural selection and genetic drift, respectively.

@@

\paragraph{Prestige bias.}
Here we introduce a new element to the model by assuming that in each generation, copiers choose their role-models one by one.
We formulate this assumption in the following.
{Denote by} $K_{i,j}$  the number of copiers that {choose} role-model $j$ after copier $i$ chose a role-model. Thus, $i$ out of $N$ copiers {had} already {chosen} a role-model, $\sum_{j=1}^N{K_{i,j}} = i$, and there are $N-i$ copiers that have yet to choose a role-model.
The stochastic process of role-model choice, 
\begin{equation} \label{eq:process}
\big\{\vec{K}_i = (K_{i,1}, \ldots, K_{i,N}) \big\}_{i=1}^N \;,
\end{equation}
is described by the recurrence equation
\begin{equation} \label{eq:recurrence}
K_{i,j} = K_{i-1,j} + S_{i,j}, \quad i,j=1,2,\ldots,N \;,
\end{equation}
where $S_{i,j}=1$ if the $i$-th copier chose role-model~$j$ and 0 otherwise, and the initial state is $K_{0,j}=0$.

Following \cref{eq:ourF}, the probability that the $i$-th copier chose role-model $j$ is given by the influence of role-model $j$ in the eyes of copier $i$,
\begin{equation}\label{eq:recPrestige}
Pr(S_{i,j}=1 \mid S_{1,j},S_{2,j},...,S_{i-1,j}) = G_{i,j} \;.
\end{equation}
The influence $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by success--the estimated biased trait value $\beta(A_{i,j})$--and prestige--the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, replacing \cref{eq:boydG} with
\begin{equation}\label{eq:prestige}
G_{i,j} = \frac{\alpha_{ij} \cdot \beta(A_{i,j}) + (1-\alpha_{ij}) \cdot K_{i-1,j}}{W_i} \;,
\end{equation}
where $W_i$ is a normalizing factor that sums the numerator over all role-models ($1\le j \le N)$ to ensure $\sum_{j=1}^{N}{G_{i,j}}=1$.

Here, the bias weight $\alpha_{i,j}$ determines the relative weighting of success and prestige bias. It is a characteristic of the interaction of role-model~$j$ with copier $i$ that determines the relative significance of direct success vs. prestige in the role-model's overall influence in the eyes of the copier.
Different individuals may evaluate the importance of success and prestige differently. Additionally, we assume each role-model displays its prestige and success individually. For example, individuals with more followers but lacking skill may emphasize the number of their followers rather than their skill.
Finally, the trait of role-model $j$ estimated by copier $i$, $A_{i,j}$, remains as in \cref{eq:relativeTrait}.

@@

(i) the expected number of copiers of role-model~$j$ equals its influence in the eyes of the first copier, multiplied by the total number of copiers, that is,
$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$); and
(ii) the expected number of copiers of each role-model equals its relative biased trait value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if the bias weight is uniform for all role-models ($\alpha=\alpha_j$ for $j=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated trait value.

@@

From \Cref{cor:GBD} we see that if there is no success bias, meaning $Q_j(1,1)=q$ for $j$ in $1,...,N$, then the expected number of copiers will be Binomial distributed. This proves that prestige bias is not frequency dependent.

@@

Frigyik et al.~\citep[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws  (the population size, $N$, in our model) approaches infinity, based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
We therefore have an approximation for the relative influence each role-model has when evaluated by copiers. Thus, choosing the role-models for all copiers is equivalent to drawing from a {multinomial} distribution where the parameters are the modified weights from a Dirichlet distribution and we have the following corollary.
\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Fixation probability and time}
After finding that the DM distribution is a good approximation of the (within-generation) role-model choice process, we turn our attention to the (between-generation) evolutionary dynamics.
We focus on the fixation probability and conditional fixation time (conditioned on the population reaching fixation) of a favored phenotype, using a diffusion-equation approximation approach, similar to analyses of population-genetic models \citep{kimura,kimura_average,otto_fixation}.
We are mainly interested in the effect of the bias weight, $\alpha$, which determines the relative effect of success and prestige on influence bias, given by \cref{eq:prestige}.
For simplicity, we use the dichotomous model, and we do not include role-model estimation error in this analysis, i.e $e_i=0$ for every copier $i$.
As shown above, transmission in our model is approximately DM distributed (\Cref{cor:dirichlet} and \cref{eq:copier_choose}).

@@

The approximation follows the trend of the simulation results for all $\alpha$ values.
{On} increasing the success coefficient {$\alpha$} to more than 0.15, the simulation results were located above the changing environment approximation, and below the constant environment approximation. We believe the reason is the structure of the cycle.
Our proof and approximation in the changing environment are for a large {number} of cycles, and when the success coefficient {$\alpha$} is too high, there might be very few cycles. Either the ideal trait is copied by enough copiers so that the prestige is sufficient to negate the success bias when the cycle changes (and the trait favored by the bias becomes the disfavored), or the opposite happens, and the ideal trait {goes} extinct before there {are} enough copiers that copied it.
We then tried to change the ratio between the number of cycles where $\hat{A}$ is favored and disfavored. We showed that the approximation fits well regardless of the ratio, but when the ratio of favored generations to disfavored ones is very high, it is very similar to a constant environment model.

@@

We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal success-bias weight, $\alpha^*$, which minimizes the expected squared error between the chosen trait value and the optimal trait value $\hat{A}$,
\begin{equation}\label{eq:optimal_alpha}
\alpha^* = \emph{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l} (\hat{A}-A_j)^2 \;,
\end{equation}
where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose role-model~$j$.
Indeed, if the trait value would have been correlated with fitness, the optimal success-bias weight would increase fitness. However in here we don't include natural selection.

@@

\begin{figure}[h]
    \includegraphics[width=\linewidth]{choose_bias.pdf}
  \caption{
  \textbf{Advantage of an optimal success-bias weight.}
  Both success-bias weight $\alpha$ (\textbf{A}) and estimation error (\textbf{B}) decrease during the role-model choosing process (within a single generation), demonstrating that prestige becomes more favored by copiers as more copiers have made their choice.
However, when $\alpha$ is homogeneous (\textbf{C}), the mean estimation error doesn't decrease, regardless of $\alpha$ or $\eta$.
The mean estimation error in the homogeneous $\alpha$ model is larger by a factor of $10$ than the optimal $\alpha$ model.
Here, population size $N=200$; estimation error is normally distributed $e \sim N(0,\eta^2)$ with standard deviation $\eta=$0.0001 (blue), 0.001 (orange), 0.01 (green), plots are average of $300$ simulations.}	
  \label{fig:influence_advantage}
\end{figure}

@@

We developed a cultural-evolution model with influence bias that includes both indirect success and prestige biases, where the latter is a bias towards role-models with many copiers.
We model these biases using a stochastic role-model choice process: each copier, in {turn}, randomly chooses a role-model, and this choice is affected both by the estimated success of each potential role-model and the number of copiers that already chose each role-model (eq.~\ref{eq:prestige}).

@@

%\paragraph{Empirical evidence of prestige bias}
Chudek et al.~\citep{prestige_cultural_learning} report the first direct tests in children that suggest the existence of prestige bias, defined as the tendency to learn from individuals to whom others have preferentially attended, learned, or deferred.
Their definition of prestige is similar to ours. They showed that the odds of 3-4 years-old children learning from an adult role-model to whom bystanders had previously preferentially attended for 10 seconds were more than twice those of learning from a role model whom bystanders ignored.
They also note that prestige effects are domain sensitive: they found that prestigious role-models were attended more when demonstrating artifact use, whereas role-models presenting food preferences had less attendants, suggesting that the domain itself (artifact use vs. food preference) can affect the attendance, and hence the prestige of the role-model.
This led to the suggestion that when the trait is costly to learn individually, prestige will have a stronger bias \citep{prestige_cultural_learning}.
It would be interesting to include costs in our model to try and observe these effects and dynamics in a large population.

@@

%\paragraph{Further work.}
One path forward is an analysis of the dynamics of the optimal success-bias weight model, in which every copier chooses its $\alpha$. It would be interesting to see the if the mean estimation error and the varying weight, $\alpha^*$, {converge} to specific values, and how they are affected by the model parameters.
It may also be possible to relax the assumptions required for our approximations, such as homogeneous estimation error and success-bias weight.
Lastly, it would be interesting to analyze the continuous model and determine how much it differs from the dichotomous model.

@@

\bibitem{prestigeSocialLearn}
Jiménez, Ángel V., and Alex Mesoudi. "Prestige-biased social learning: Current evidence and outstanding questions." Palgrave Communications 5.1 (2019).

\bibitem{rethinkPrestige}
Chellappoo, Azita. "Rethinking prestige bias." Synthese 198.9 (2021): 8191-8212.

@@

\begin{proof}
The initial influence of role-model $j$ based on \cref{eq:prestige} is
\begin{equation}\label{eq:initial_prob}
G_{1,j} = \frac{\alpha_j\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N} \alpha_m\cdot\beta(A_m+e)} \;.
\end{equation}
The denominator of \cref{eq:initial_prob} can also be formulated as:
\begin{equation}\label{eq:denominator}
 \sum\limits_{m=1}^{N}\alpha_m\beta(A_m+e) = N \cdot \overline{\alpha \cdot \beta(A+e)} \;,
\end{equation}
where $\overline{\alpha\beta(A+e)}$ is the mean value of $\alpha_m\cdot\beta(A_m+e)$.
Using \cref{eq:denominator} and \textbf{Corollary 1} we get,
\begin{equation}
\E[K_{N,j}] = \alpha_j \cdot \beta(A_j+e) \bigg/ \overline{\alpha \cdot \beta(A+e)} \;,
\end{equation}
\end{proof}
